\documentclass{article}

\usepackage[margin=1in]{geometry} 
\usepackage{amsmath, amsthm, amssymb, hyperref}

\newcommand{\R}{\mathbb{R}}  
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\D}{\mathbb{D}}
\newcommand{\bH}{\mathbb{H}}

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\brac}[1]{\left[ #1 \right]}
\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\norm}[1]{\left\Vert #1 \right\Vert}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\iprod}[2]{\left\langle #1, #2 \right\rangle}


\DeclareMathOperator{\real}{Re}
\DeclareMathOperator{\imag}{Im}

\newcommand{\comp}[2]{#1 \circ #2}

\DeclareMathOperator{\dom}{dom}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}
\newenvironment{definition}{\begin{proof}[Definition]}{\end{proof}}

% lol, lmao
\linespread{1.1}
\renewcommand{\baselinestretch}{1.17}

% from 117
    % \newenvironment{practice}
    % [2]{\begin{trivlist}
    % \item[\hskip \labelsep {\bfseries     
    % % "debug mode": for working on it
    % % Practice #1, Week #2.
    % % "release mode": for submitting
    % Week #2: Practice #1.
    % }\hskip \labelsep]}{\end{trivlist}}
    
\begin{document}

% 117
\renewcommand{\labelenumi}{(\alph{enumi})}

% ------------------------------------------ %
%                 START HERE                 %
% ------------------------------------------ %

\title{Homework 4} % Replace with appropriate title
\author{Nathaniel Hamovitz\\Math 118A, Ponce, F22}
\date{due 2022-10-25}

\maketitle

\textbf{1. }
Consider $\R$ with the usual distance. Using only the definition, prove

\begin{enumerate}
    \item  % ✅
    $A = [0, 1)$ is not compact.
    \begin{proof}
        Consider the open cover $\set{\sigma_n}_{n \in \N}$, where $\sigma_n = \paren{-\frac{1}{2}, 1 - \frac{1}{n}}$. As the infimum of each interval remains constant and the supremum is increasing we have that $\forall n \in \N, \sigma_n \subsetneq \sigma_{n + 1}$. 
        
        Given any finite subcover $\set{\sigma_{n_i}}$, we can consider $j = \max \set{n_i}$. From above, we see that $\cup_{n_i} \sigma_{n_i} \subseteq \sigma_j$. But there must exist $x \in [0, 1)$ such that $x \notin \sigma_j$; consider $x = 1 - \frac{1}{2j}$. 

        Hence there is at least one open cover of $A$ from which it is not possible to extract a finite subcover, and so $A$ is not compact.
    \end{proof}


    \item  % ✅ but could be touched up
    $D = \set{1 + \frac{(-1)^{n}}{n} : n \in \N} \cup \set{1}$ is compact.
    \begin{proof}
        Let $\set{\sigma_\alpha}_{\alpha \in I}$ be an open covering of $D$. Then there must be some open set $\sigma_0$ such that $1 \in \sigma_0$. 

        $\sigma_0$ contains all but finitely many elements of $D$; each remaining element must be contained in some set $\sigma_n$. There are finitely many, so considering those $\sigma_n$ along with $\sigma_0$ gives us a finite subcovering of $D$.        
    \end{proof}
\end{enumerate}


\newpage % ---


\textbf{2. }  % ✅
Prove that if $A_1, \dots, A_n, \dots$ is a countable collection of countable sets, then
$$\bigcup_{n = 1}^{\infty} A_n \qquad \text{is also countable.}$$

\begin{proof}
    % line em up and diagonals!
    % Diagonals!! I don't want to draw the picture!!
    % you can also do a hilbert curve! (is that what it's called?)

    Let $\displaystyle U = \bigcup_{n = 1}^\infty A_n$.
    
    Write each $A_n$ in a row, like so (here the exponent is index within each set):
    \begin{align*}
        A_1 &= \set{a_1^1, a_1^2, a_1^3, \dots, a_1^n, \dots} \\
        A_2 &= \set{a_2^1, a_2^2, a_2^3, \dots, a_2^n, \dots} \\
        A_3 &= \set{a_3^1, a_3^2, a_3^3, \dots, a_3^n, \dots}
    \end{align*}
    
    Now consider the function/sequence $f: \N \mapsto U$ constructed by drawing arrows from top right to bottom left, so that (for example)
    
    \begin{align*}
        f(1) &= a_1^1 \\
        f(2) &= a_1^2 \\
        f(3) &= a_2^1 \\
        f(4) &= a_1^3 \\
        f(5) &= a_2^2 \\
        f(6) &= a_3^1
    \end{align*}
    
    and so on. Then $f$ puts $U$ in bijection with the naturals, and so $U$ is countable. (Note that for it to be a true bijection, you must skip any $a_i^j$ you have previously encountered when constructing the sequence.)
\end{proof}



\newpage % ---


\textbf{3. } % ✅
Consider $\R^n$ with the usual distance. Prove that if $A \subset
% ❔: possibly-equal or strict subset?
\R^n$ is uncountable, then $A' \ne \emptyset$ (i.e. the set of limit points of $A$ is nonempty).

\begin{proof}
    % Malik did this in OH Day 4-2, starting from the version of B-W Ponce proved in class

    First we place an open ball of radius $1$ around every rational. Clearly their union is the whole space; that is,
    $$\R^n = \bigcup_{n = 1}^\infty B_1(q_n)$$
    where $\Q^n = \bigcup_{n = 1}^\infty \set{q_n}$.

    Suppose for a contradiction that $A \cap B_1(q_n)$ is finite for all $n \in N$. Note that 
    \begin{align*}
        A &= A \bigcap \R^n \\
        &= A \bigcap \brac{\bigcup_{n = 1}^\infty B_1(q_n)} \\
        &= \bigcup_{n = 1}^\infty \brac{A \bigcap B_1(q_n)},
    \end{align*}
    which is the countable union of finite sets. By the previous problem, that implies $A$ is finite or countable. However, we know $A$ is uncountable, and so we have a contradiction. Hence there must exist $n_0 \in \N$ such that $A \cap B_1(q_n)$ is infinite (in fact, that it is uncountable).

    Note that
    $$A \cap B_1(q_{n_0}) \subseteq B_1(q_{n_0}) \subsetneq \ol{B_1(q_{n_0})}.$$
    Then by Bolzano-Weierstrass $(A \cap B_1(q_{n_0}))' \ne \emptyset$.

    We now prove a lemma: for any sets $A, B \subseteq X$, $A \subseteq B$ implies $A' \subseteq B'$. Let $x \in A'$. Then $\forall r > 0, B_r(x) \cap A - \set{x} \ne \emptyset$. Because $A \subseteq B$, $B_r(x) \cap A \subseteq B_r(x) \cap B$ and so we have $\forall r > 0, B_r(x) \cap B - \set{x} \ne \emptyset$. Thus $x \in B'$ and $A' \subseteq B'$.

    Now note that $A \cap B_1(q_{n_0}) \subseteq A$, so by the above lemma $(A \cap B_1(q_{n_0}))' \subseteq A'$. The smaller set is nonempty and so the larger must be as well; $A' \ne \emptyset$.
\end{proof}


\newpage % ---


\textbf{4. } % ✅
Consider $\R^2$ with the usual distance, and define
$$E = \set{\paren{\sin(n), \cos(m)} : n, m \in \Z}$$

Prove that $E' \ne \emptyset$.

\begin{proof}
    Let $B = [-1, 1] \times [-1, 1]$. Clearly $E \subsetneq B$. $B$ is closed and bounded in $\R^2$ and so by Heine-Borel compact.

    Consider the function $f : \N \mapsto \R^2$ where $f(n) = \paren{\sin n, \cos 0} = \paren{\sin n, 1}$. $f$ is an injective map because $\sin a = \sin b$ iff $a - b = 2 \pi k$ for some $k \in \Z$, and no natural numbers are a multiple of $2\pi$ apart (if two were, then $\pi$ could be written as a rational number). Therefore $f[\N]$ is infinite. Now notice that $f[\N] \subsetneq E$, and hence $E$ is infinite.

    We now apply the Bolzano-Weierstrass theorem. $E$ is an infinite set and a subset of a compact set, and therefore $E' \ne \emptyset$.    
\end{proof}


\newpage % ---


\textbf{5. } % ✅ 
% ❗ could elaborate on (c) though
Let $K_1, \dots, K_n, \dots$ be a family of compact subsets of $\R^n$ considered with the usual distance.
\begin{enumerate}
    \item  % ✅
    Is $K_1 \cup K_2$ compact?

    Yes.
    \begin{proof}
        Let $\set{\sigma_\alpha}_{\alpha \in I}$ be an open covering of $K_1 \cup K_2$. Because $K_1$ and $K_2$ are both compact, it is possible to extract finite subcoverings $\set{\sigma_{\alpha_i}}_{i = 1}^N$ and $\set{\sigma_{\alpha_j}}_{j = 1}^M$ such that $\displaystyle K_1 \subseteq \cup_{i = 1}^N \sigma_{\alpha_i}$ and $\displaystyle K_2 \subseteq \cup_{j = 1}^M \sigma_{\alpha_j}$. Thus
        $$\displaystyle K_1 \cup K_2 \subseteq \brac{\cup_{i = 1}^N \sigma_{\alpha_i}} \cup \brac{\cup_{j = 1}^M \sigma_{\alpha_j}}$$
        and as both those collections are finite, so is their union.
    \end{proof}


    \item % ✅
    Is $\bigcup_{n = 1}^\infty K_n$ compact?

    No.
    \begin{proof}
        Consider $K_n = \ol{B_1(q_n)}$, where $\Q^n = {q_1, q_2, \dots}$. Each $K_n$ is closed and bounded, and thus compact, but their union is $\R^n$, which is open and not bounded and so not compact.
        
    \end{proof}


    \item 
    Is $\bigcap_{n = 1}^\infty K_n$ compact?

    Yes.
    \begin{proof}
        (A more general proof using the definition of compactness is possible, but if we restrict ourself to $\R^n$, the proof becomes simple.)

        Each $K_n$ is closed and bounded, because it is compact.
        
        By definition of boundedness, $\exists x \in \R^n, \exists M \in \R, K_1 \subseteq B_M(x)$. By definition of intersection, $\cap_{n = 1}^\infty K_n \subseteq K_1 \subseteq B_M(x)$ and hence the intersection is bounded.

        The intersection, including the infinite intersection, of closed sets is closed; hence $\cap_{n = 1}^\infty K_n$ is closed.

        Therefore by Heine-Borel $\cap_{n = 1}^\infty K_n$ is compact.        
    \end{proof}
\end{enumerate}

% suggested exercises: Rudin Ch 2, 19 and 22




\end{document}